### 2022-02-28 doc/src/VSLevel.tex
Clarify when to raise exceptions when hvictl.VTI = 1

When bit VTI (Virtual Trap Interrupt control) =~1, attempts from
\mbox{VS-mode} to explicitly access CSRs \z{sip}, \z{sie}, or, for RV32
only, \z{siph} or \z{sieh}, cause a virtual instruction exception.
Furthermore, when VTI =~1, a virtual instruction exception is raised
also for any attempt by the guest to write to a CSR that might
cause a bit of \z{vsip}/\z{vsiph} to change from one to zero,
excluding bit~9 for external interrupts (SEIP).
In particular, if register \z{vstimecmp} is implemented
(from extension Sstc), then attempts from \mbox{VS-mode}
to write to \z{stimecmp} or (RV32 only) \z{stimecmph}
cause a virtual instruction exception when VTI~=~1.

>>>>

When bit VTI (Virtual Trap Interrupt control) =~1, attempts from
\mbox{VS-mode} to explicitly access CSRs \z{sip}, \z{sie}, or, for RV32
only, \z{siph} or \z{sieh}, cause a virtual instruction exception.
Furthermore, for any given CSR, if there is some circumstance in which
a write to the register may cause a bit of \z{vsip}/\z{vsiph} to change
from one to zero, excluding bit~9 for external interrupts (SEIP),
then when VTI =~1, a virtual instruction exception is raised
also for any attempt by the guest to write this register.
Both the value being written to the CSR and the value of
\z{vsip}/\z{vsiph} (before or after) are ignored for determining
whether to raise the exception.
(Hence a write would not actually need to change a bit of
\z{vsip}/\z{vsiph} from one to zero for the exception to be raised.)
In particular, if register \z{vstimecmp} is implemented
(from extension Sstc), then attempts from \mbox{VS-mode}
to write to \z{stimecmp} or (RV32 only) \z{stimecmph}
cause a virtual instruction exception when VTI~=~1.
